---
title: "Consillient Assessment"
author: "Chetan"
date: "11/03/2022"
output:
  html_document: default
  pdf_document: default
---



```{r libraries}
library(readxl)
library(tidyverse)
library(rstatix)
```


```{r data load}
data <- read_excel("./data.xlsx")
```

## Descritive Statitics

```{r pressure, echo=FALSE}

table(data$`Do you know anyone - or have you heard about anyone - who is a victim of rape or`, useNA = "always")

table(data$random_half, useNA = "always")

data = rename(data, children_girls = `How many of your children are girls?`,
              education = `What is the highest level of schooling you have completed?`,
              female_police = `As far as you know, are there any female police officers in the closest police s`,
              hh_size = `How many members, INCLUDING YOURSELF, are part of your household?`,
              land_own_in = `Do you and your husband own land in ${district_label} ?`,
              marital_status = `What is your marital status?`,
              police_loc = `Do you know where the nearest police station or police post is?`,
              time_here = `How long have you lived in ${district_label} ?`,
              walk_night = `Do you feel comfortable walking around this area alone at night?`,
              known_victim = `Do you know anyone - or have you heard about anyone - who is a victim of rape or`)

#data$dv_ideal_outcome1_lab


# Create a new data frame which is required for analysis
data_new <- data %>% dplyr::select("age", "children_girls", "education", "female_police", "hh_size", "idp", "land_own_in", "majority", "marital_status", "police_loc", "rural", "time_here", "walk_night", "known_victim", "sgbv_ideal_outcome1_lab", "dv_ideal_outcome1_lab","random_half")
```


```{r}
#class(data_new$random_half)
#unique(data_new$random_half)

# Random half
data_new$random_half[which(data_new$random_half == '0. sgbv')] <- "sgbv"
data_new$random_half[which(data_new$random_half == '1. dv')] <- "dv"

# Female police
data_new$female_police[which(data_new$female_police == '0. No')] <- "No"
data_new$female_police[which(data_new$female_police == '1. Yes')] <- "Yes"
data_new$female_police[which(data_new$female_police == '98. Don\'t know')] <- "Don\'t know"

# Education
data_new$education[which(data_new$education == '6. College and above')] <- "College and above"
data_new$education[which(data_new$education == '0. None')] <- "None"
data_new$education[which(data_new$education == '1. Madrassa only')] <- "Madrassa"
data_new$education[which(data_new$education == '3. Completed Primary')] <- "Completed Primary"
data_new$education[which(data_new$education == '2. Some Primary')] <- "Some Primary"
data_new$education[which(data_new$education == '5. Completed Secondary')] <- "Completed Secondary"
data_new$education[which(data_new$education == '4. Some Secondary')] <- "Some Secondary"


# land own in
data_new$land_own_in[which(data_new$land_own_in == '1. Yes')] <- "Yes"
data_new$land_own_in[which(data_new$land_own_in == '0. No')] <- "No"

# marital status
data_new$marital_status[which(data_new$marital_status == '1. Married')] <- "Married"
data_new$marital_status[which(data_new$marital_status == '2. Single')] <- "Single"
data_new$marital_status[which(data_new$marital_status == '3. Divorced')] <- "Divorced"
data_new$marital_status[which(data_new$marital_status == '5. Separated')] <- "Separated"
data_new$marital_status[which(data_new$marital_status == '4. Widow/widower')] <- "Widow/widower"
data_new$marital_status[which(data_new$marital_status == '99. Refused to answer')] <- "Refused to answer"


# police loc
data_new$police_loc[which(data_new$police_loc == '1. Yes')] <- "Yes"
data_new$police_loc[which(data_new$police_loc == '0. No')] <- "No"

# time here
data_new$time_here[which(data_new$time_here == '3. More than 5 years')] <- "More than 5 years"
data_new$time_here[which(data_new$time_here == '2. 1-5 years')] <- "1-5 years"
data_new$time_here[which(data_new$time_here == '1. Less than one year')] <- "Less than one year"
data_new$time_here[which(data_new$time_here == '98. Don\'t know')] <- "Don\'t know"

## Walk Night
data_new$walk_night[which(data_new$walk_night == '2. Yes')] <- "Yes"
data_new$walk_night[which(data_new$walk_night == '0. No')] <- "No"
data_new$walk_night[which(data_new$walk_night == '1. Sometimes')] <- "Sometimes"

## Known victims
data_new$known_victim[which(data_new$known_victim == '1. Yes')] <- "Yes"
data_new$known_victim[which(data_new$known_victim == '0. No')] <- "No"

# sgbv_ideal_outcome
data_new$sgbv_ideal_outcome1_lab[which(data_new$sgbv_ideal_outcome1_lab == 'Dambiilaha waa la ciqaabay')] <- "The offender is punished"
data_new$sgbv_ideal_outcome1_lab[which(data_new$sgbv_ideal_outcome1_lab == 'Qofka dhibanaha ahi magdhow ayaa la siiyey ama waa la caawiyey ama dhaawacii loo geystay ayaa dib loo hagaajiyay.')] <- "The individual victim is compensated or made whole or supported"
data_new$sgbv_ideal_outcome1_lab[which(data_new$sgbv_ideal_outcome1_lab == 'Qoyska/kooxda dhibbanaha waxaa la siiyay magdhow ama dhaawacii loo geystay ayaa dib loo hagaajiyay ama waa la taageeray.')] <- "The victim's family / group is compensated or made whole or supported"

data_new <- data_new[-(which(data_new$sgbv_ideal_outcome1_lab == 'qofk dhibanaag magdhow yalasiiy mise wal caawii mise dhaawici linjeysadi wal haagajiiy')),]
  


# dv_ideal_outcome1_lab
data_new$dv_ideal_outcome1_lab[which(data_new$dv_ideal_outcome1_lab == 'Qofka dhibanaha ahi magdhow ayaa la siiyey ama waa la caawiyey ama dhaawacii loo geystay ayaa dib loo hagaajiyay.')] <- "The individual victim is compensated or made whole or supported"
data_new$dv_ideal_outcome1_lab[which(data_new$dv_ideal_outcome1_lab == 'Dambiilaha waa la ciqaabay')] <- "The offender is punished"
data_new$dv_ideal_outcome1_lab[which(data_new$dv_ideal_outcome1_lab == 'Qoyska/kooxda dhibbanaha waxaa la siiyay magdhow ama dhaawacii loo geystay ayaa dib loo hagaajiyay ama waa la taageeray.')] <- "The victim's family / group is compensated or made whole or supported"

# Deleting na from random half
colSums(is.na(data_new))


unique(data_new$dv_ideal_outcome1_lab)

# Making factors
data_new$known_victim <- as.factor(data_new$known_victim)
data_new$walk_night <- as.factor(data_new$walk_night)
data_new$time_here <- factor(data_new$time_here, levels = c("Don't know","Less than one year","1-5 years","More than 5 years"), ordered = T)

data_new$police_loc <- as.factor(data_new$police_loc)
data_new$marital_status <- as.factor(data_new$marital_status)
data_new$land_own_in <- as.factor(data_new$land_own_in)
data_new$education <- factor(data_new$education, levels = c("None", "Madrassa", "Some Primary", "Completed Primary", "Some Secondary", "Completed Secondary", "College and above"), ordered = T)
data_new$female_police <- as.factor(data_new$female_police)
data_new$random_half <- as.factor(data_new$random_half)
data_new$idp <- as.factor(data_new$idp)
data_new$rural <- as.factor(data_new$rural)
data_new$majority <- as.factor(data_new$majority)
data_new$sgbv_ideal_outcome1_lab <- as.factor(data_new$sgbv_ideal_outcome1_lab)
data_new$dv_ideal_outcome1_lab <- as.factor(data_new$dv_ideal_outcome1_lab)
str(data_new)

#class(data_new$time_here)

data.group.random.half <- group_by(data_new, random_half)
#get_summary_stats(data.group.random.half, children_girls, type = "mean_sd")

table(data.group.random.half$random_half, data.group.random.half$female_police)

```


```{r}
summary(data_new)
```




```{r}
data_sgbv <- filter(data_new, random_half == 'sgbv')

#table(data.group.random.half$random_half, data.group.random.half$known_victim)
# table(data.group.random.half$random_half, data.group.random.half$female_police)
# table(data.group.random.half$random_half, data.group.random.half$time_here)

```
```{r}
#ggplot(data_sgbv, aes(x = walk_night, y = age)) + geom_bar(aes(fill = majority), stat = "identity", color = "white",position = position_dodge(0.9))+facet_grid(~marital_status) 

# table_sgbv_rural_time <- table(data_sgbv$rural, data_sgbv$time_here)
# 
# addmargins(table_sgbv_rural_time)
# addmargins(prop.table(table_sgbv_rural_time))


table_sgbv_rural_police <- table(data_sgbv$rural, data_sgbv$police_loc)

addmargins(table_sgbv_rural_police)
addmargins(prop.table(table_sgbv_rural_police))
```

```{r}
chisq.test(data_sgbv$rural, data_sgbv$police_loc)
```
Based on the results of the chi-square test generated above, p-value is 0.014, which is less than 0.05. This implies that there is a statistically significant relationship between the rural and police_loc variable.



```{r}
# sgbv_table <- data_sgbv %>% count(rural, time_here, sort = TRUE)
# sgbv_table

sgbv_table <- data_sgbv %>% count(police_loc, rural, sort = TRUE)
sgbv_table

# ggplot(data = data_sgbv) + 
#   geom_bar(mapping = aes(x = time_here,  fill = rural), position = "dodge")

ggplot(data = data_sgbv) + 
  geom_bar(mapping = aes(x = police_loc,  fill = rural), position = "dodge")
```

From the above bar graph it is evident that people who have stayed more than 5 years in urban area know more about sgbv cases. Also, people who live in urban areas and has a police station nearby also knows more about such cases.


## Question 2:

```{r}
(ideal_random_table <- data_new %>% count(sgbv_ideal_outcome1_lab, dv_ideal_outcome1_lab, random_half, sort = TRUE))

ideal_random_table_new <- ideal_random_table[!with(ideal_random_table,is.na(dv_ideal_outcome1_lab)& is.na(sgbv_ideal_outcome1_lab)),]

```


```{r}
for(i in 1:length(ideal_random_table_new$sgbv_ideal_outcome1_lab)){
  
    if(!is.na(ideal_random_table_new$sgbv_ideal_outcome1_lab[i])){
        ideal_random_table_new$dv_ideal_outcome1_lab[i] <-  ideal_random_table_new$sgbv_ideal_outcome1_lab[i]
  }
}

ideal_random_table_new <- ideal_random_table_new[,-1]
names(ideal_random_table_new) <-  c("ideal_outcome1_lab","random_half","n")
names(ideal_random_table_new)
#length(ideal_random_table_new)
#require(cowplot)
# (plot1 <- ggplot(data = data_new) + 
#   stat_count(mapping = aes(x = dv_ideal_outcome1_lab)))
# (plot2 <- ggplot(data = data_new) + 
#   stat_count(mapping = aes(x = sgbv_ideal_outcome1_lab)))
#plot_grid(plot1, plot2, labels = "AUTO")


ideal_random_table_new



str(ideal_random_table_new)


```

```{r}
ggplot(data = ideal_random_table_new) + 
  geom_bar(mapping = aes(x = random_half,y = n, fill = ideal_outcome1_lab), position = "dodge", stat = "identity")
```


## Answer 3



```{r}
(data_majority_table <- data.frame(table(data.group.random.half$random_half, data.group.random.half$majority)))


ggplot(data = data_majority_table) + 
  geom_bar(mapping = aes(x = Var2 ,y = Freq, fill = Var1), position = "dodge", stat = "identity")
```

From the above bar graph it, we can see non-majority people in the clan are more tend to dv and sgbv then majority people.
